---
title: "data import"
author: "Chunmei Li"
date: "2017年6月6日"
output: 
  html_document: 
    keep_md: yes
---
```{r}
library(tidyverse)
```

```{r}
#no path
#heights <- read_csv("data/heights.csv")
```

```{r}
read_csv("a,b,c
1,2,3
4,5,6")
```
```{r}
read_csv("The first line of metadata
  The second line of metadata
  x,y,z
  1,2,3", skip = 2)
```

```{r}
read_csv("# A comment I want to skip 
x,y,z
  1,2,3", comment = "#")
```

```{r}
read_csv("1,2,3\n4,5,6", col_names = FALSE)
```

```{r}
read_csv("1,2,3\n4,5,6", col_names = c("x", "y", "z"))
```

```{r}
read_csv("a,b,c\n1,2,.", na = ".")
```


read_csv() reads comma delimited files, read_csv2() reads semicolon separated files (common in countries where , is used as the decimal place), read_tsv() reads tab delimited files, and read_delim() reads in files with any delimiter.

read_fwf() reads fixed width files. You can specify fields either by their widths with fwf_widths() or their position with fwf_positions(). read_table() reads a common variation of fixed width files where columns are separated by white space.

read_log() reads Apache style log files. (But also check out webreadr which is built on top of read_log() and provides many more helpful tools.)

11.2.2 Exercise

1.
read_delim

2.

```{r}
?read_csv
```
col_names, col_types, locale, na, quoted_na, quote, trim_ws, n_max, guess_max, progress

3.

```{r}
?read_fwf
```

fwf_widths

4.

```{r}
read_delim("x,y\n1,'a,b'", delim=",", quote="\'")
```

5.

```{r}
read_csv("a,b\n1,2,3\n4,5,6") #lost the third element
read_csv("a,b,c\n1,2\n1,2,3,4") #add NA to 1st row, and lost the 4th element in 2nd row
read_csv("a,b\n\"1") #double-quote
read_csv("a,b\n1,2\na,b") # integer 1 and 2 become character.
read_csv("a;b\n1;3") # 1 element, a;b is column name, 1;3 is value
```


```{r}
str(parse_logical(c("TRUE", "FALSE", "NA")))

str(parse_integer(c("1", "2", "3")))

str(parse_date(c("2010-01-01", "1979-10-14")))
```

```{r}
parse_integer(c("1", "231", ".", "456"), na = ".")
```

```{r}
x <- parse_integer(c("123", "345", "abc", "123.45"))
x
```
```{r}
problems(x)
```
```{r}
parse_double("1.23")
```

```{r}
parse_double("1,23", locale = locale(decimal_mark = ","))
```

```{r}
parse_number("$100")

parse_number("20%")

parse_number("It cost $123.45") #different output from book

```

```{r}
# Used in America
parse_number("$123,456,789")


# Used in many parts of Europe
parse_number("123.456.789", locale = locale(grouping_mark = "."))


# Used in Switzerland
parse_number("123'456'789", locale = locale(grouping_mark = "'"))

```

```{r}
charToRaw("Hadley")
```

```{r}
x1 <- "El Ni\xf1o was particularly bad this year"
x2 <- "\x82\xb1\x82\xf1\x82\xc9\x82\xbf\x82\xcd"

x1

x2
#???
```

```{r}
parse_character(x1, locale = locale(encoding = "Latin1"))

parse_character(x2, locale = locale(encoding = "Shift-JIS"))

```

```{r}
guess_encoding(charToRaw(x1))

guess_encoding(charToRaw(x2))
```

```{r}
fruit <- c("apple", "banana")
parse_factor(c("apple", "banana", "bananana"), levels = fruit)
```

```{r}
parse_datetime("2010-10-01T2010")

parse_datetime("20101010")
```

```{r}
parse_date("2010-10-01")
```

```{r}
library(hms)
parse_time("01:10 am")

parse_time("20:10:01")
```

```{r}
parse_date("01/02/15", "%m/%d/%y")

parse_date("01/02/15", "%d/%m/%y")

parse_date("01/02/15", "%y/%m/%d")
```

```{r}
parse_date("1 janvier 2015", "%d %B %Y", locale = locale("fr"))
date_names_langs()
```

```{r}
parse_date("2017年6月6日", "%Y %m %d", locale = locale("zh"))
```


11.3.5 Exercise

1.
```{r}
?locale
```
decimal_mark, grouping_mark, encoding

2.
```{r}
#parse_double("1,23", locale = locale(decimal_mark = ",", grouping_mark = ","))
#Error: `decimal_mark` and `grouping_mark` must be different
```

```{r}
parse_number("123,456", locale=locale(decimal_mark=","))
#"," became into decimal mark
```
```{r}
parse_number("123.456", locale=locale(grouping_mark="."))
#"." became into grouping mark
```

3.

```{r}
parse_date("2015/02/19", locale=locale(date_format = "%Y/%m/%d"))

parse_time("06/24/46", locale=locale(time_format = "%H/%M/%S"))
```

4.

??

5.

read_csv() reads comma "," delimited files, read_csv2() reads semicolon ";" separated files (common in countries where , is used as the decimal place)

```{r}
read_csv("x,y,z\n4,5,6", col_names =T)

read_csv2("x;y;z\n4;5;6", col_names = T)
```

6.

d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"

```{r}
d1 <- parse_date("January 1, 2010", "%B %d, %Y")
d1
```

```{r}
d2 <- parse_date("2015-Mar-07", "%Y-%b-%d")
d2
```

```{r}
d3 <- parse_date("06-Jun-2017", "%d-%b-%Y")
d3
```

```{r}
d4 <- parse_date(c("August 19 (2015)", "July 1 (2015)"), "%B %d (%Y)")
d4
```

```{r}
d5 <- parse_date("12/30/14", "%m/%d/%y")
d5
```

```{r}
t1 <- parse_time("1705", "%H%M")
t1
```

```{r}
t2 <- parse_time("11:15:10.12 PM", "%I:%M:%OS %p")
t2
```

