---
title: "May31"
author: "Chunmei Li"
date: "2017年5月30日"
output: 
  html_document: 
    keep_md: yes
---
7.6
```{r}
library(tidyverse)
ggplot(data = faithful) + 
  geom_point(mapping = aes(x = eruptions, y = waiting))
```

```{r}
#???
library(modelr)

mod <- lm(log(price) ~ log(carat), data = diamonds)

diamonds2 <- diamonds %>% 
  add_residuals(mod) %>% 
  mutate(resid = exp(resid))

ggplot(data = diamonds2) + 
  geom_point(mapping = aes(x = carat, y = resid))
```

```{r}
ggplot(data = diamonds2) + 
  geom_boxplot(mapping = aes(x = cut, y = resid))
```
7.7
```{r}
ggplot(data = faithful, mapping = aes(x = eruptions)) + 
  geom_freqpoly(binwidth = 0.25)
```

```{r}
ggplot(faithful, aes(eruptions)) + 
  geom_freqpoly(binwidth = 0.25)
```

```{r}
diamonds %>% 
  count(cut, clarity) %>% 
  ggplot(aes(clarity, cut, fill = n)) + 
    geom_tile()
```
8.1
Press Cmd/Ctrl + Shift + F10 to restart RStudio.
Press Cmd/Ctrl + Shift + S to rerun the current script.
8.2
 always using the Linux/Mac style with forward slashes.
 never use absolute paths in your scripts.
 
 
 
```{r}
library(tidyverse)

ggplot(diamonds, aes(carat, price)) + 
  geom_hex()
ggsave("diamonds.pdf")

write_csv(diamonds, "diamonds.csv")
```


Create an RStudio project for each data analysis project.

Keep data files there; we’ll talk about loading them into R in data import.

Keep scripts there; edit them, run them in bits or as a whole.

Save your outputs (plots and cleaned data) there.

Only ever use relative paths, not absolute paths.


10.

```{r}
as_tibble(iris)
```

```{r}
tibble(
  x = 1:5, 
  y = 1, 
  z = x ^ 2 + y
)
```

```{r}
tb <- tibble(
  `:)` = "smile", 
  ` ` = "space",
  `2000` = "number"
)
tb
```

```{r}
tribble(
  ~x, ~y, ~z,
  #--|--|----
  "a", 2, 3.6,
  "b", 1, 8.5
)
```

```{r}
tibble(
  a = lubridate::now() + runif(1e3) * 86400,
  b = lubridate::today() + runif(1e3) * 30,
  c = 1:1e3,
  d = runif(1e3),
  e = sample(letters, 1e3, replace = TRUE)
)
```

```{r}
nycflights13::flights %>% 
  print(n = 10, width = Inf)
```

```{r}
nycflights13::flights %>% 
  View()
```

```{r}
df <- tibble(
  x = runif(5),
  y = rnorm(5)
)
df
#$ and [[. [[ can extract by name or position; $ only extracts by name but is a little less typing.
df$x
df[["x"]]
df[[1]]
```

```{r}
#use these in a pipe, you’ll need to use the special placeholder .:
df %>% .$x
df %>% .[["x"]]
```

```{r}
class(as.data.frame(tb))
```

10.5 Exercise
1.
```{r}
mtcars
class(mtcars)
class(nycflights13::flights)
```
2.
```{r}
df <- data.frame(abc = 1, xyz = "a")
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

```{r}
#tibble
df1<- tibble(abc=1, xyz="a")
df1
df1$x
df1[,"xyz"]
df1[,c("abc", "xyz")]
```
3.
$mpg or [["mpg"]]

4.
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

1.
```{r}
annoying$`1`
#or
annoying[["1"]]
```

2.
```{r}
ggplot(annoying, aes(x=`1`, y=`2`))+geom_point()


```

```{r}
annoying <- annoying %>%
  mutate(`3`=`2`/`1`)
annoying
```
4.
```{r}
annoying <- rename(annoying, one = `1`, two = `2`, three = `3`)
annoying
```
5.
```{r}
?tibble::enframe
#Converting atomic vectors to data frames

#enframe(x, name = "name", value = "value")
```

6.

```{r}
#???
```

