---
title: "R-club-May-10"
author: "Chunmei Li"
date: "2017年5月6日"
output: 
  html_document: 
    keep_md: yes
---
5.1.1 prerequisites
```{r}
#install.packages("nycflights13")
library(nycflights13)
library(tidyverse)
```
5.2
```{r}
flights #time_hour is not dttm
```
```{r}
filter(flights, month == 1, day == 1)
jan1 <- filter(flights, month == 1, day == 1)
(dec25 <- filter(flights, month == 12, day == 25)) #save and print the filterred result
```
5.2.1
```{r}
#filter(flights, month = 1)
```

```{r}
sqrt(2) ^ 2 == 2

1/49 * 49 == 1
#can’t store an infinite number of digits!
```
```{r}
# use near to compare
near(sqrt(2) ^ 2,  2)

near(1 / 49 * 49, 1)
```
```{r}
filter(flights, month == 11 | month == 12) #don't use filter(flights, month == 11 | 12) to find Nov or Dec
```

```{r}
nov_dec <- filter(flights, month %in% c(11, 12))
```

```{r}
filter(flights, !(arr_delay > 120 | dep_delay > 120))
filter(flights, arr_delay <= 120, dep_delay <= 120)

#how about filter(flights, arr_delay <= 120 & dep_delay <= 120)
```
```{r}
NA > 5

10 == NA

NA + 10

NA / 2

NA == NA

# Let x be Mary's age. We don't know how old she is.
x <- NA

# Let y be John's age. We don't know how old he is.
y <- NA

# Are John and Mary the same age?
x == y

# We don't know!

# use is.na to determine if a value is missing
is.na(x)


```

```{r}
df <- tibble(x = c(1, NA, 3))
filter(df, x > 1)

filter(df, is.na(x) | x > 1)

```

5.2.4 Exercise
1.
```{r}
#Had an arrival delay of two or more hours
filter(flights, arr_delay >= 120)
#Flew to Houston (IAH or HOU)
filter(flights, dest %in% c("IAH", "HOU"))
#Were operated by United, American, or Delta
filter(flights, carrier %in% c("UA", "AA", "DL"))
#Departed in summer (July, August, and September)
filter(flights, month %in% c(7:9))
#Arrived more than two hours late, but didn’t leave late
filter(flights, dep_delay <= 0 & arr_delay > 120)
#Were delayed by at least an hour, but made up over 30 minutes in flight
filter(flights, dep_delay >= 60 &  dep_delay - arr_delay > 30)
#Departed between midnight and 6am (inclusive)
filter(flights, dep_time==2400 & dep_time <= 0600)# summary flights, the max of dep_time is 2400.

```
2.Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
```{r}
?between()#This is a shortcut for x >= left & x <= right
filter(flights, between(dep_time,0,600))
```
3.How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
sum(is.na(flights$dep_time))
filter(flights, is.na(dep_time))# dep_delay, arr_time, and arr_delay are missing. these rows might present the flights cancelled.

```
4.Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)
```{r}
is.na(NA^0) # NA is an unkown number??
is.na(NA|TRUE)# because NA|TRUE is TRUE
is.na(FALSE&NA)# always FALSE
is.na(NA*0)# inf*0
```
5.3
```{r}
arrange(flights, year, month, day)
```

```{r}
arrange(flights, desc(arr_delay))
```

```{r}
# NA always at the end
df <- tibble(x = c(5, 2, NA))
arrange(df, x)
arrange(df, desc(x))
```
5.3.1 Exercise
```{r}
#1. How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).
arrange(df, desc(is.na(x)), x)
arrange(flights, desc(is.na(dep_time)), dep_time)
```
2.
```{r}
#2.Sort flights to find the most delayed flights. Find the flights that left earliest.
arrange(flights, desc(dep_delay)) #
arrange(flights, dep_time)#
```
3.
```{r}
#3. Sort flights to find the fastest flights.
arrange(flights, desc(distance/air_time))
```
4.
```{r}
#4.Which flights travelled the longest? Which travelled the shortest?
arrange(flights, desc(distance))
arrange(flights,distance)
```
5.4
```{r}
select(flights, year, month, day)
select(flights, year:day)
```

```{r}
#select except from year to day
select(flights, -(year:day))
```

```{r}
rename(flights, tail_num = tailnum)
```

```{r}
select(flights, time_hour, air_time, everything())
```
5.4.1 Exercise
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, starts_with("dep_"), starts_with("arr_"))
#select(flights, contains("dep_"), contains("arr_", ignore.case = F)) will have other variables containing ...
select(flights, matches("^dep|arr_time|delay$"))#??
```
2.
```{r}
# 2. What happens if you include the name of a variable multiple times in a select() call?
select(flights, dep_time, dep_time, dep_time)
```
3.What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
select(flights, one_of(c("dep_time", "dep_delay", "arr_time", "arr_delay")))
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars)) #is.in
```
4.Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("time", ignore.case = F))# R is sensitive to capital and lowercase.
```
5.5
```{r}
flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60
)
```

```{r}
# can refer to variables just created.
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```
```{r}
#keep the new variables
transmute(flights,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```

```{r}
#calcuate hour and minutes
transmute(flights,
  dep_time,
  hour = dep_time %/% 100,
  minute = dep_time %% 100
)
```
```{r}
#offset
(x <- 1:10)
#>  [1]  1  2  3  4  5  6  7  8  9 10
lag(x)
#>  [1] NA  1  2  3  4  5  6  7  8  9
lead(x)
```

```{r}
x
#>  [1]  1  2  3  4  5  6  7  8  9 10
cumsum(x)
#>  [1]  1  3  6 10 15 21 28 36 45 55
cummean(x)
#>  [1] 1.0 1.5 2.0 2.5 3.0 3.5 4.0 4.5 5.0 5.5
#install.packages("RcppRoll")

```

```{r}
#Ranking

```
5.5.2 Exercise
```{r}
#1.
mutate(flights, dep_time_minutes=dep_time %/% 100*60 + dep_time %% 100, sched_dep_time_minutes=sched_dep_time %/% 100*60 + sched_dep_time %% 100)
```

```{r}
#2.
transmute(flights, air_time, arr_time - dep_time)# they are not the same
transmute(flights, air_time, arr_time_dep_time = (arr_time %/% 100*60 + arr_time %% 100) - (dep_time %/% 100*60 + dep_time %% 100))# ?? time difference??
```

3.
```{r}
select(flights, contains("dep", ignore.case = F))
#dep_delay = dep_time -sched_dep_time
#need to convert to minutes
```
4.
```{r}
mutate(flights, -min_rank(dep_delay))
arrange(flights, min_rank(desc(dep_deplay)))
```
5.
```{r}
1:3 + 1:10
# add vector 1:3 with vector 1:10 one by one until there is no more number in the latter one.
```

6.
```{r}
?Trig
#cos(x)
#sin(x)
#tan(x)

#acos(x)
#asin(x)
#atan(x)
#atan2(y, x)

#cospi(x)
#sinpi(x)
#tanpi(x)
```

```{r}
x <- 1:10

```

