---
title: "tidy data part1"
author: "Chunmei Li"
date: "2017年6月13日"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
```

```{r}
table1
```

```{r}
table2
```
```{r}
table3
```

```{r}
table4a
```
```{r}
table4b
```

```{r}
table1 %>% 
  mutate(rate = cases / population * 10000)
```
```{r}
table1 %>% 
  count(year, wt = cases)
```

```{r}
library(ggplot2)
ggplot(table1, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```


12.2.1 Exercise
1.

table1: each variable has own column, each observation has own row, each value has own cell.
table2: type contains 2 variables, cases and populations; each observation has own row
table3: rate contains 2 variables, cases and populations which were not shown in table;
table4: variable cases and populations are into table4a and table4b, separately.


2.





3.

```{r}
table2 %>% 
  filter(type == "cases") %>%
  ggplot(aes(year, count)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```

```{r}
table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")
```

```{r}
table4b %>% 
  gather(`1999`, `2000`, key = "year", value = "population")
```

```{r}
tidy4a <- table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")
tidy4b <- table4b %>% 
  gather(`1999`, `2000`, key = "year", value = "population")
left_join(tidy4a, tidy4b)
```

```{r}
spread(table2, key = type, value = count)
```
12.3 Exercise
1.
```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`)
```
year became into character, should be numeric.

```{r}
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`, convert = TRUE)
```

2.

1999 and 2000 are non-syntactic names in R, and need to be surrounded with ``.


3.





4.

```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
```

yes.

```{r}
preg%>%
  gather(male, female, key="gender", value=cases)
```

```{r}
preg %>% gather(male, female, key="gender", value=cases) %>%
  spread(key = pregnant, value=cases)
```


```{r}
table3 %>% 
  separate(rate, into = c("cases", "population"))
```

```{r}
table3 %>% 
  separate(rate, into = c("cases", "population"), sep = "/")
```

```{r}
table3 %>% 
  separate(rate, into = c("cases", "population"), convert = TRUE)
```

```{r}
table3 %>% 
  separate(year, into = c("century", "year"), sep = 2)
```

```{r}
table5 %>% 
  unite(new, century, year)
```

```{r}
table5 %>% 
  unite(new, century, year, sep = "")
```

12.4.3 Exercise

1.

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra="merge")
```
```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three", "four"), fill="left")
```


2.remove	
If TRUE, remove input column from output data frame.


