---
title: "R-club-Apr-26"
author: "Chunmei Li"
date: "042417"
output: 
  html_document: 
    keep_md: yes
---
#install.packages
```{r}
#learning ggplot2
#install.packages("tidyverse")
library(tidyverse)
#use data frame mpg
mpg
?mpg
ggplot(data = mpg) +geom_point(mapping = aes(x = displ, y = hwy))
```
#graphing template
#ggplot(data = <DATA>) + <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
#exercise
#run
```{r}
ggplot(data = mpg)#empty plots
mtcars
nrow(mtcars)#32 rows
ncol(mtcars)#11 colums
?mpg#`drv` describe "f = front-wheel drive, r = rear wheel drive, 4 = 4wd"
#scatterplot of `cty` vs `hwy`
ggplot(data = mpg) +geom_point(mapping = aes(x = cty, y = hwy))
#scatterplot of `class` vs `drv`
ggplot(data = mpg) +geom_point(mapping = aes(x = class, y = drv))# because `class` and `drv` are not continuous variables.
```
#the differences by using color, size, alpha, shape
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = class))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = class))
#transparency
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, alpha = class))
#shape
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, shape = class))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
#Exersize 1
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
#because to set an aesthetic manually, we should set the aesthetic by name as an argument of geom function, not inside of `aes()`
```
#2 manufacturer, model, trans, drv, fl, year and class are categorical, cyl, cty, and hwy are continuous. when the classify of variables is `chr`, the variables are categorical, and when the classify of variable is `int`, `dbl`, or `dbl`, the variables are continous.
#3 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = cty))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = cty))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, shape = cty))
#`color` and `size` can be used for mapping continous variable with graduated color or size, but `shape` can not be used for mapping continous variable.

```
#4 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = hwy, size = class))
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = displ))
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = hwy, color = class))
# it seems that it doesn't matter??? no new information can be revealed

```
#5
```{r}
?geom_point#`stroke` is used to modify the width of the border and works with the shapes with border.
```
#6
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = cty < 20))
# the plots will be divided into 2 logical groups by 2 different colors.
```

#3.5
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(. ~ cyl)
```
#3.5.1 Exercise
#1
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(. ~ cty)
#plots would be faceted into many grids or wraps.
```
#2
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)#the empty cells mean no data was recorded under this combination of `drv` and `cyl`.
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))# the empty cells above are corresponding to the empty plots in this plot.
```
#3
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)#plot the relationship between `displ` and `hwy` in each `drv` displayed by rows.

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)#plot the relationship between `displ` and `hwy` in each `cyl` displayed by columns.

#`.` means columns or rows are not defined.

```
#4 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color=class))
# the relationship between `displ` and `hwy` in each `class` would be more clear, but the whole relationship between `displ` and `hwy` is not clear.
```
#5
```{r}
?facet_wrap#Number of rows and columns.`as.table` also control the layout of the individual lanes
?facet_grid#number of rows and columns depend on the variables in dataset.
```
#6
while using `facet_grid()`, if put the variables with less unique levels, the plots would be faceted into many grids, it would not be useful for analyzing.

